%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Michal Rostecki} & Email: \href{mailto:michal.rostecki@gmail.com}{michal.rostecki@gmail.com}\\
  & Mobile: +49-162-970-7248 \\
  & \href{https://github.com/mrostecki}{https://github.com/mrostecki} \\
  & \href{https://build.opensuse.org/users/mrostecki}{https://build.opensuse.org/users/mrostecki} \\
  & \href{https://www.linkedin.com/in/michal-rostecki-b3968372/}{https://www.linkedin.com/in/michal-rostecki-b3968372/}
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SUSE}{Remote, Berlin, Germany}
      {Software Engineer}{Jan 2018 - Present}
      \resumeItemListStart
        \resumeItem{\href{https://cilium.io/}{Cilium}}
          {Open source software which provides networking and security for
            application containers, using the Linux kernel technology called
            eBPF. Contributing upstream to \underline{\href{https://github.com/cilium/cilium/pulls/mrostecki}{Cilium}} and \underline{\href{https://lore.kernel.org/bpf/?q=mrostecki}{bpftool}}. Integrating
            Cilium with SUSE product (SUSE CaaS Platform). Investigating customer bugs and providing necessary fixes or/and backports for Cilium, bpftool, iproute2 and BPF subsystem.}
        \resumeItem{\href{https://github.com/SUSE/skuba}{SUSE CaaS Platform}}
          {Kubernetes distribution based on SUSE Enterprise Linux and kubeadm. Responsible for integrating
            Cilium with SUSE CaaSP. \underline{\href{https://github.com/SUSE/skuba/pulls?q=author\%3Amrostecki}{My contribution}}.}
        \resumeItem{openSUSE}
          {Maintaining packages in the distribution: bazel, boringssl,
            bpftool, c-lightning, firewalld, grpc, libbpf. \underline{\href{https://build.opensuse.org/users/mrostecki}{My activity}}.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Kinvolk}{Berlin, Germany}
      {Software Engineer}{Dec 2016 - Dec 2017}
      \resumeItemListStart
        \resumeItem{rktlet}
          {Kubernetes runtime server using rkt as a container
            engine. \underline{\href{https://github.com/kubernetes-retired/rktlet/pulls?q=author\%3Anhlfr}{My
            contribution}}.}
        \resumeItem{aws-operator}
          {Kubernetes operator for deploying the other Kubernetes clusters on
            Amatzon EC2
            instances. \underline{\href{https://github.com/giantswarm/aws-operator/pulls?q=author\%3Anhlfr}{My contribution}}.}
        \resumeItem{Endless OS}
          {Linux distribution. I was responsible for implementing flatpak
            images for \underline{\href{https://github.com/endlessm/firefox-flatpak}{Firefox}} and \underline{\href{https://github.com/endlessm/vlc-flatpak}{VLC}}.}
      \resumeItemListEnd

    \resumeSubheading
      {Mirantis}{Poznan, Poland}
      {Software Engineer}{Aug 2015 - Nov 2016}
      \resumeItemListStart
        \resumeItem{Kubernetes}
          {\underline{\href{https://bit.ly/3nQ1Fs6}{Upstream contribution}}, mostly bugfixes.}
        \resumeItem{Virtlet}
          {Kubernetes runtime server which allows to run virtual machines
            based on QCOW2 images. Responsible for the initial
            implementation, responsible for the part which manages virtual
            machines and images via libvirt. \underline{\href{https://bit.ly/34XDgIE}{My contribution}}.}
        \resumeItem{OpenStack Kolla}
          {Project which deploys OpenStack in Docker
            containers. \underline{\href{https://bit.ly/319lxwI}{Contributed
              upstream}}. Worked on the
            \underline{\href{https://opendev.org/x/kolla-mesos/src/commit/a0ffda04aedf02fb2ed10218b87b4ed4eb5aa5f7}{kolla-mesos}}
            subproject, which was deploying OpenStack on top of Mesos
            clusters. Implemented multi-node deployment and orchestration of
            different OpenStack components by roles.}
      \resumeItemListEnd

    \resumeSubheading
      {Allegro}{Poznan, Poland}
      {Cloud Software Engineer}{Nov 2014 - Aug 2015}
      \resumeItemListStart
        \resumeItem{OpenStack, OpenContrail}
          {Deployment, maintenance and bugfixing the OpenStack and
            OpenContrail cluster. Made contributions to \underline{\href{https://bit.ly/2H1kQP5}{several OpenStack projects}} and \underline{\href{https://bit.ly/3o3ZnWy}{OpenContrail}}.}
        \item{Developing internal tools integrating internal CI with Mesos and Marathon, written in Python.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Interests}

Free and Open Source Software, video games, music, cryptocurrencies, traveling, running, swimming

%-------------------------------------------
\end{document}
